Supplementary Materials And Methods

### 2019-09-30 NAR_form_article.tex
Figure defining

miRNA and target pairs per line should be provided as edge list to
construct the network. At each line minimum required information is
expression levels of miRNA and the target. If available, additional data
about factors effecting binding or efficiency of miRNA can be provided
as separate columns (see Figure S1 in Supplementary Tables). After
construction of the network, amount of miRNA per target is calculated
and kept as edge data. Simply, a target will sequester miRNA
proportional to its ratio amount among other targets. If additional
criteria effecting the binding of miRNA to its target is provided,
distribution of miRNA will be calculated accordingly. Target can be mRNA
or any other ceRNA (circRNA, ncRNA, etc.) thus, throughout the
manuscript terms target, gene and ceRNA are used interchangeably.

@@

Initially, the network is assumed in steady-state (Figure
\ref{fig:fig1}A) condition and needs least one trigger for initiating
calculations. The trigger can be a change in expression level of one or
more genes (Figure \ref{fig:fig1}B). After a trigger, the network
undergoes iterative cycle of calculations at each of which distribution
of miRNA in local neighborhood is recalculated (Figure \ref{fig:fig1}C).
Based on new miRNA distribution, expression level of each node
(i.e.~ceRNA) is updated. This update results in change of expression
value of common target (G4) in system. In this case, the common target
acts as trigger for the other group (the targets interacted with M2
miRNA) in the network. Due to common targeted elements, the change in
one neighborhood spreads to other neighborhoods (Figure
\ref{fig:fig1}D), consequently have potential to affect whole network
due to ``ripple effect'' (see Section 2 in Supplementary Materials and
Methods).

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=10cm]{Fig1.jpg}
\end{center}
\caption{Schematic presentation of mechanism of network based model. 
    \textbf{A)} In steady state, miRNAs (M: triangles) repress targets (G: circles) according to proportion of target expression level. 
    \textbf{B)} Two fold increase in transcript level of Gene2 (G2) acts as a trigger (shown in red). 
    \textbf{C)} Distribution of miRNA1 (M1) changes. 
    \textbf{D)} The change at expression of common target affects changes of proportional distribution of miRNA2 (M2). Expression values are rounded to integers for simplicity. Gray values on edges indicate initial distribution, red values indicate increase and blue values indicate decrease in distribution. Shades of circles indicate different levels of increase.}
\label{fig:fig1}
\end{figure*}

@@

Interactions between miRNAs and their targets can be affected from
various factors. So, our model integrates multiple factors when
calculating overall miRNA activity. We classified factors into two
categories. Binding factors determine interaction between miRNA and
target and they alter amount of miRNA sequestered to target. Efficiency
factors dictate degradation efficiency of miRNA on its target and define
amount of target to be degraded. In other words, binding factors exert
their influence before or during binding, efficiency factors exert their
influence after binding. In the literature, binding free energy
\citetext{\citealp[
]{cao_predicting_2012}; \citealp{helwak_mapping_2013}} and seed type
\citep{werfel_preferential_2017} in miRNA:target interactions are
described as factors effecting binding affinity. Also, binding region
(e.g, 5'UTR, 3'UTR, CDS) was shown to drastically affect miRNA
degradation efficiency
\citep{hausser_analysis_2013, helwak_mapping_2013}. Since binding or
degradation efficiency from literature have various and broad ranges,
both binding and efficiency factors are normalized to their maximum
values and scaled to {[}0,1{]} interval. The normalized values of
factors are used to determine binding activity and miRNA efficiency on
targets (Figure \ref{fig:fig2}). Binding affinities (activity, \(Eff\))
of miRNAs on each individual gene are calculated as shown in equation
\eqref{eq:3}; \(C_m\), miRNA expression in the group; \(C_{gi}\),
individual gene expression; gi, individual gene (Figure
\ref{fig:fig2}C).

@@

Not all miRNA:target binding events result in degradation of target. The
degradation of target by bound miRNA depends on efficiency factors such
as binding region. Exact repression efficiency of miRNA is calculated
according to equation \eqref{eq:4} (Figure \ref{fig:fig2}D);
\(RE^\prime_{gi}\), normalized values of region efficiency coefficient
between miRNA and gene. The cooperative repression activity of miRNAs to
their common targets is figured out as shown in Figure \ref{fig:fig2}E
(see Section 3 in Supplementary Materials and Methods).

@@

We have applied our model in a real dataset for which experimental
measurements of various factors were available. Expression levels of
miRNA and genes in tumor and normal tissue of single patient are
retrieved from TCGA Research Network \url{https://www.cancer.gov/tcga}.
High-throughput experimental datasets which are provided miRNA:gene
target pairs with interaction factors
\citep{helwak_mapping_2013, moore_mirnatarget_2015} (Detailed codes are
available at Section 6 in Supplementary Materials and Methods). We have
combined miRNA and gene expression datasets via miRNA:target gene
dataset retrieved from published datasets
\citep{helwak_mapping_2013, moore_mirnatarget_2015}. Detailed
description of network construction and its code is available in
Supplementary Materials and Methods. SERPINE2, one of the most effective
nodes, has been used as trigger in ceRNA network simulation in breast
cancer patient network. Relevant steps and codes are available at
Supplementary Materials and Methods.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=8cm]{Fig3.jpg}
\end{center}
\caption{Target regulations with interaction parameters. 
     \textbf{A)} In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. 
     \textbf{B)} The changes the repression activities after increasing of G2 expression. 
     \textbf{C)} Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). 
     \textbf{D)} Regulation of gene expression of other gene group via triggering target (common target between M1 and M2)}
\label{fig:fig3}
\end{figure*}

@@

Earlier studies reported that miRNA regulatory interactions are affected
by different parameters. For example, Xu et al.~have investigated the
importance of seed pairing type between miRNAs and their targets and
target site location by using proteomics dataset
\citep{xu_characterization_2014}. They have proposed that the features
of binding between miRNA and target can be critical for miRNA
efficiency. In addition, binding energy between miRNA and targets is a
significant determinant for miRNA efficiency and it has been reported
that strength of miRNA:target interactions is depended on binding energy
of complexes \citep{breda_quantifying_2015}. Similarly, another study
revealed that affinity is correlated with seed pairing of miRNA:target
pairs and suggested that affinity is correlated with number of canonical
seed base pairing \citep{bosson_endogenous_2014}. Therefore, we have
integrated aforementioned interaction parameters that could be useful
for predicting miRNA repression activity more accurately. The sample
dataset used in Figure \ref{fig:fig1} is recalculated with additional
factors Table \ref{tab:one} in effect with same trigger, two fold
increase in Gene2 (Figure \ref{fig:fig3}). When the factors were taken
into account in the system, miRNA efficiencies varied as shown in Figure
\ref{fig:fig3}A. Although the miRNA:target expression ratios in
steady-state were same in comparison with the sample dataset without
factors, efficiency of binding and repression have changed. On the other
hand, changes in expression levels of G4 and G1 differ although they
have same initial conditions (Detailed codes are available at Sections
3-4 in Supplementary Materials and Methods). This is due to fact that G4
is targeted by two miRNAs, M1 and M2 (Figures \ref{fig:fig3}D) and
changed interaction factors.

@@

In regulation of miRNA target sample system (Figure \ref{fig:fig3}),
miRNA (M1) repressive efficiency on the primary triggering gene (G2) is
low in steady-state. So it has been observed that the regulatory
activities of miRNA on the targets are weak after the increase of miRNA
target G2. When model is triggered with two fold increase in expression
level of common target (G4), more prominent changes were observed in
gene expression levels in network compared to changes caused by G2
increase. Furthermore, change in expression level of target gene that
has strong miRNA repression efficiency resulted in evident perturbation
in network. On the other hand, it was observed that Gene2 was weakly
affected from change of Gene4 expression because of its weak interaction
factors. Since perturbation efficiency of each gene is different, we
have developed a function which screens each gene in the network for
their perturbation efficiencies (Detailed codes are available at Section
4 in Supplementary Materials and Methods). On the other hand, when we
applied the method on the minimal dataset (i.e.~Gene4 is trigger
element), Gene4 has been found to be the most efficient element in terms
of number of perturbed elements and miRNA2 (M2) has been found to be
causing the highest mean in expression changes.

@@

We have analysed the realistic network in context of perturbation
efficiencies of nodes. This process were run with 3 fold upregulation
and 10 iteration in conditions where elements that have less than five
percent change are not taken into account (Codes are found at Section
6.5 in Supplementary Materials and methods). With this approach, SERPINE
is found as one of the most effective gene nodes in network. We have
observed that the results of simulation with SERPINE2 gene, a serine
protease inhibitor, one of the overexpressed genes of breast cancer
\citep{yang2018expression, candia2006protease} is not convenient with
tumor tissue expression values, when we compared the tumor gene
expression dataset retrieved from TCGA and simulation results obtained
via our approach (see Section 6.6 in Supplementary Materials and
methods). Simulation results were not expected to be consistent with
tumor tissue expression values because large number of abnormal
regulations were observed in these tissues. So, it might not said that a
single gene is responsible for entire regulations in cancer cells.
Besides, the all other factors such as up/down regulation of miRNAs or
other genes were ignored. Therefore, it would be more useful to test our
approach with an ideal dataset that includes entire informations of gene
expression values before and after the regulation of a known gene at
existing tissue, and miRNA expression values of this tissue at initial
conditions.

>>>>

miRNA and target pairs per line should be provided as edge list to
construct the network. At each line minimum required information is
expression levels of miRNA and the target. If available, additional data
about factors effecting binding or efficiency of miRNA can be provided
as separate columns (see Table S1 in Supplementary Tables). After
construction of the network, amount of miRNA per target is calculated
and kept as edge data. Simply, a target will sequester miRNA
proportional to its ratio amount among other targets. If additional
criteria effecting the binding of miRNA to its target is provided,
distribution of miRNA will be calculated accordingly (available at Table
S6 in Supplementary Tables). Target can be mRNA or any other ceRNA
(circRNA, ncRNA, etc.) thus, throughout the manuscript terms target,
gene and ceRNA are used interchangeably.

@@

Initially, the network is assumed in steady-state (Figure
\ref{fig:fig1}A and Figure S2) condition and needs least one trigger for
initiating calculations. The trigger can be a change in expression level
of one or more genes (Figure \ref{fig:fig1}B and Figure S3). After a
trigger, the network undergoes iterative cycle of calculations at each
of which distribution of miRNA in local neighborhood is recalculated
(Figure \ref{fig:fig1}C and Figure S4A). Based on new miRNA
distribution, expression level of each node (i.e.~ceRNA) is updated.
This update results in change of expression value of common target (G4)
in system. In this case, the common target acts as trigger for the other
group (the targets interacted with M2 miRNA) in the network. Due to
common targeted elements, the change in one neighborhood spreads to
other neighborhoods (Figure \ref{fig:fig1}D and Figure S4B),
consequently have potential to affect whole network due to ``ripple
effect'' (see Section 2 in Supplementary Materials and Methods).

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=10cm]{Fig1.jpg}
\end{center}
\caption{Schematic presentation of mechanism of network based model. 
    (\textbf{A}) In steady state, miRNAs (M: triangles) repress targets (G: circles) according to proportion of target expression level. 
    (\textbf{B}) Two fold increase in transcript level of Gene2 (G2) acts as a trigger (shown in red). 
    (\textbf{C}) Distribution of miRNA1 (M1) changes. 
    (\textbf{D)}) The change at expression of common target affects changes of proportional distribution of miRNA2 (M2). Expression values are rounded to integers for simplicity. Gray values on edges indicate initial distribution, red values indicate increase and blue values indicate decrease in distribution. Shades of circles indicate different levels of increase.}
\label{fig:fig1}
\end{figure*}

@@

Interactions between miRNAs and their targets can be affected from
various factors. So, our model integrates multiple factors when
calculating overall miRNA activity. We classified factors into two
categories. Binding factors determine interaction between miRNA and
target and they alter amount of miRNA sequestered to target. Efficiency
factors dictate degradation efficiency of miRNA on its target and define
amount of target to be degraded. In other words, binding factors exert
their influence before or during binding, efficiency factors exert their
influence after binding. In the literature, binding free energy
\citep{cao_predicting_2012, helwak_mapping_2013} and seed type
\citep{werfel_preferential_2017} in miRNA:target interactions are
described as factors effecting binding affinity. Also, binding region
(e.g, 5'UTR, 3'UTR, CDS) was shown to drastically affect miRNA
degradation efficiency
\citep{hausser_analysis_2013, helwak_mapping_2013}. Since binding or
degradation efficiency from literature have various and broad ranges,
both binding and efficiency factors are normalized to their maximum
values and scaled to {[}0,1{]} interval. The normalized values of
factors are used to determine binding activity and miRNA efficiency on
targets (Figure \ref{fig:fig2}). Binding affinities (activity, \(Eff\))
of miRNAs on each individual gene are calculated as shown in equation
\eqref{eq:3}; \(C_m\), miRNA expression in the group; \(C_{gi}\),
individual gene expression; gi, individual gene (Figure
\ref{fig:fig2}C).

@@

Not all miRNA:target binding events result in degradation of target. The
degradation of target by bound miRNA depends on efficiency factors such
as binding region. Exact repression efficiency of miRNA is calculated
according to equation \eqref{eq:4} (Figure \ref{fig:fig2}D);
\(RE^\prime_{gi}\), normalized values of region efficiency coefficient
between miRNA and gene. The cooperative repression activity of miRNAs to
their common targets is figured out as shown in Figure \ref{fig:fig2}E.

@@

We have applied our model in a real dataset for which experimental
measurements of various factors were available. Expression levels of
miRNA and genes in tumor and normal tissue of single patient are
retrieved from TCGA Research Network \url{https://www.cancer.gov/tcga}.
High-throughput experimental datasets which are provided miRNA:gene
target pairs with interaction factors
\citep{helwak_mapping_2013, moore_mirnatarget_2015} (Detailed codes are
available at Section 6 in Supplementary Materials and Methods). We have
combined miRNA and gene expression datasets via miRNA:target gene
dataset retrieved from published datasets
\citep{helwak_mapping_2013, moore_mirnatarget_2015} (Section 6 in
Supplementary Materials and Methods and Table S4 in Supplementary
Tables). SERPINE2, one of the most effective nodes, has been used as
trigger in ceRNA network simulation in breast cancer patient network.
Relevant steps and codes are available at Supplementary Materials and
Methods.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[width=15cm,height=8cm]{Fig3.jpg}
\end{center}
\caption{Target regulations with interaction parameters. 
     (\textbf{A}) In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. 
     (\textbf{B}) The changes the repression activities after increasing of G2 expression. 
     (\textbf{C}) Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). 
     (\textbf{D}) Regulation of gene expression of other gene group via triggering target (common target between M1 and M2)}
\label{fig:fig3}
\end{figure*}

@@

Earlier studies reported that miRNA regulatory interactions are affected
by different parameters. For example, Xu et al.~have investigated the
importance of seed pairing type between miRNAs and their targets and
target site location by using proteomics dataset
\citep{xu_characterization_2014}. They have proposed that the features
of binding between miRNA and target can be critical for miRNA
efficiency. In addition, binding energy between miRNA and targets is a
significant determinant for miRNA efficiency and it has been reported
that strength of miRNA:target interactions is depended on binding energy
of complexes \citep{breda_quantifying_2015}. Similarly, another study
revealed that affinity is correlated with seed pairing of miRNA:target
pairs and suggested that affinity is correlated with number of canonical
seed base pairing \citep{bosson_endogenous_2014}. Therefore, we have
integrated aforementioned interaction parameters that could be useful
for predicting miRNA repression activity more accurately. The sample
dataset used in Figure \ref{fig:fig1} is recalculated with additional
factors Table \ref{tab:one} in effect with same trigger (Detailed codes
can be found at Section 3 in Supplementary Materials and Methods), two
fold increase in Gene2 (Figure \ref{fig:fig3}B, and Figure S6). When the
factors were taken into account in the system, miRNA efficiencies varied
as shown in Figure \ref{fig:fig3}A (Figure S5). Although the
miRNA:target expression ratios in steady-state were same in comparison
with the sample dataset without factors, efficiency of binding and
repression have changed. On the other hand, changes in expression levels
of G4 (Detailed codes are available at Section 4 in Supplementary
Materials and Methods; and Figure S8) and G1 differ although they have
same initial conditions. This is due to fact that G4 is targeted by two
miRNAs, M1 and M2 (Figures \ref{fig:fig3}D) and changed interaction
factors.

@@

In regulation of miRNA target sample system (Figure \ref{fig:fig3} and
Figure S5-7), miRNA (M1) repressive efficiency on the primary triggering
gene (G2) is low in steady-state. So it has been observed that the
regulatory activities of miRNA on the targets are weak after the
increase of miRNA target G2. When model is triggered with two fold
increase in expression level of common target (G4), more prominent
changes were observed in gene expression levels in network compared to
changes caused by G2 increase. Furthermore, change in expression level
of target gene that has strong miRNA repression efficiency resulted in
evident perturbation in network. On the other hand, it was observed that
Gene2 was weakly affected from change of Gene4 expression because of its
weak interaction factors. Since perturbation efficiency of each gene is
different, we have developed a function which screens each gene in the
network for their perturbation efficiencies. When we applied the method
on the minimal dataset (i.e.~Gene4 is trigger element), Gene4 has been
found to be the most efficient element in terms of number of perturbed
elements and miRNA2 (M2) has been found to be causing the highest mean
in expression changes (see Section 5 in Supplementary Materials and
Methods).

@@

We have analysed the realistic network in context of perturbation
efficiencies of nodes. This process were run with 3 fold upregulation
and 10 iteration in conditions where elements that have less than five
percent change are not taken into account (Codes are found at Section
6.5 in Supplementary Materials and methods). With this approach,
SERPINE2 has been found as one of the most effective gene nodes in
network. We have observed that gaining steady-state in realistic network
takes a lot of time because of complex interactions, as expected, and
SERPINE2 exhibit highest efficiency at iteration 31 with given
conditions (see Section 6.6 in Supplementary Materials and Methos and
Figure S9 in Supplementary Figures). We ran the model with two fold of
iteration which is observed as most effective. We have observed that the
results of simulation with SERPINE2 gene, a serine protease inhibitor,
one of the overexpressed genes of breast cancer
\citep{yang2018expression, candia2006protease} is not convenient with
tumor tissue expression values, when we compared the tumor gene
expression dataset retrieved from TCGA and simulation results obtained
via our approach (see Section 6.6 in Supplementary Materials and
methods). Simulation results were not expected to be consistent with
tumor tissue expression values because large number of abnormal
regulations were observed in these tissues. So, it might not said that a
single gene is responsible for entire regulations in cancer cells.
Besides, the all other factors such as up/down regulation of miRNAs or
other genes were ignored. Therefore, it would be more useful to test our
approach with an ideal dataset that includes entire informations of gene
expression values before and after the regulation of a known gene at
existing tissue, and miRNA expression values of this tissue at initial
conditions.

### 2019-09-30 Supplementary_figures.Rmd
article NAR form
scanning
Figure defining

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2,  fig.show='hold', fig.cap = "Sequential iteration of minsamp data. a) First response of system to Gene2 upregulation (2nd iteration). b) Spreading of perturbation on system (3th iteration)", fig.subcap= NULL}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle=1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "a)")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "b)")

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Sequential iteration of minsamp data with interaction factors a)First response of system to Gene2 upregulation (2nd iteration). b)Spreading of perturbation on system (3th iteration)"}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "a)")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "b)")

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Perturbation of Gene4 on minsamp data with interaction factors. a) Netwrk at steady-state. b) Upregulation of Gene4. c) Primary response of network to upregulation of Gene4. d) Re-regulation of whole nodes on system (3th iteration)"}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "a)")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "b)")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "c)")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "d)")
```

@@

```{r}
E9GE_mirnagenenormal<-readRDS("data/E9GE_mirnagenenormal.rda")
head(E9GE_mirnagenenormal)
```

>>>>

```{r}
minsamp<-readRDS("data/minsamp.RDS")
```

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2,  fig.show='hold', fig.cap = "Sequential iteration of minsamp data. A) First response of system to Gene2 upregulation (2nd iteration). B) Spreading of perturbation on system (3th iteration)", fig.subcap= NULL}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle=1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "A")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "B")

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Sequential iteration of minsamp data with interaction factors A)First response of system to Gene2 upregulation (2nd iteration). B)Spreading of perturbation on system (3th iteration)"}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "A")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "B")

@@

```{r, message=FALSE, warning=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Perturbation of Gene4 on minsamp data with interaction factors. A) Network at steady-state. B) Upregulation of Gene4. C) Primary response of network to upregulation of Gene4. D) Re-regulation of whole nodes on system (3th iteration)"}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "A")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "B")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "C")

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "D")
```

@@

```{r}
E9GE_mirnagenenormal<-readRDS("data/E9GE_mirnagenenormal.RDS")
head(E9GE_mirnagenenormal)
```

### 2019-09-30 Supplementary_mat_met.Rmd
Figure defining

# 1. Functions defined for ceRNA models and workflow of method
We defined the functions that can be used with R programming. Briefly, these functions process a given miRNA:gene dataset and convert to graph object. All values that are significant in miRNA:target interactions are stored in edge variables and processed with formulations that are given in previous section. The functions and steps of approach are explained as following (Figure S1 in Supplementary Figures) :

@@

@@

So, we offered an approach about to find iteration. `find_iteration` function does not give the iteration to gain steady-state, but it gives the iteration which has maximum affected node counts. The function is applied as following:

>>>>

# 1. Functions defined for ceRNA models and workflow of method

We defined the functions that can be used with R programming. Briefly, these functions process a given miRNA:gene dataset and convert to graph object. All values that are significant in miRNA:target interactions are stored in edge variables and processed with formulations that are given in previous section. The functions and steps of approach are explained as following (Figure S1 in Supplementary Figures) :

@@

 A part of dataset can be found at Table S4 in Supplementary Tables.

@@

So, we offered an approach about to find iteration. `find_iteration` function does not give the iteration to gain steady-state, but it gives the iteration which has maximum affected node counts . The function is applied as following:
